A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface\tnoteref{t1}

### 2022-03-29 sections/queueing_model/blocking_time/main.tex
Apply suggestion by alex
Investigate the truncation effect (#34)
* Get initial plots of truncation effects

Plots added on unbounded simulation VS Markov chain (while
increasing capacity):
- Waiting time
- Blocking time
- Proportion of individuals within time

* Add bounded simulation to same plot

* Write script to generate duration for each method

* Get timing data when M=50

Times for N = (10, 30, 50, inf) for markov (waiting, blocking and
proportion formula) and simulation (1 trial, 20 trials)

* Get timing data when M=5

Times for N = (10, 30, 50, inf) for markov (waiting, blocking and
p

Figure \ref{fig:markov_vs_des_blocking_time_comparison} illustrates a comparison 
between the formulas that arise from the Markov chain model and the equivalent 
values of the blocking time extracted from discrete event simulation
(appendix~\ref{sec:appendix_des}).
The blocking time is calculated using both methods for a range of values of
\(\lambda_2\).
The figure is used to demonstrate the accuracy of the blocking time formula of
the constructed queueing model as well as the effect of truncating the model.
The simulation was ran 100 times and the recorded mean blocking time at each 
iteration is used to populate the violin plots.
Similar to figure \ref{fig:markov_vs_des_waiting_time_comparison_overall}, these
plots shows a comparison between the calculated mean blocking time using Markov 
chain, using a truncated simulation and using a simulation with infinite
capacity (without the artificial parameters \(N\) and \(M\)).
The blocking times generated by the truncated simulation match the ones
generated by the Markov chains model.
Note that this comparison includes just type 2 individuals since type 1 
individuals cannot be blocked.

>>>>

Figure \ref{fig:markov_vs_des_blocking_time_comparison} illustrates a comparison 
between the formulas that arise from the Markov chain model and the equivalent 
values of the blocking time extracted from discrete event simulation
(appendix~\ref{sec:appendix_des}).
The blocking time is calculated using both methods for a range of values of
\(\lambda_2\).
The figure is used to demonstrate the accuracy of the blocking time formula of
the constructed queueing model as well as the effect of truncating the model.
The simulation was ran 100 times and the recorded mean blocking time at each 
iteration is used to populate the violin plots.
Similar to figure \ref{fig:markov_vs_des_waiting_time_comparison_overall}, these
plots shows a comparison between the calculated mean blocking time using Markov 
chain, using a truncated simulation and using a simulation without the
artificial parameters \(N\) and \(M\).
The blocking times generated by the truncated simulation match the ones
generated by the Markov chains model.
Note that this comparison includes only type 2 individuals since type 1 
individuals cannot be blocked.

### 2022-03-29 sections/queueing_model/proportion_within_target/main.tex
Investigate the truncation effect (#34)
* Get initial plots of truncation effects

Plots added on unbounded simulation VS Markov chain (while
increasing capacity):
- Waiting time
- Blocking time
- Proportion of individuals within time

* Add bounded simulation to same plot

* Write script to generate duration for each method

* Get timing data when M=50

Times for N = (10, 30, 50, inf) for markov (waiting, blocking and
proportion formula) and simulation (1 trial, 20 trials)

* Get timing data when M=5

Times for N = (10, 30, 50, inf) for markov (waiting, blocking and
proportion formula) and si

Figure \ref{fig:markov_vs_des_proportion_comparison_overall} shows a comparison
of the mean proportion of individuals within target when using Markov chains 
and discrete event simulation (appendix~\ref{sec:appendix_des}).
The figure is used to demonstrate the accuracy of the formula for the 
proportion of individuals within time of the constructed queueing model
as well as the effect that truncating the model has on the formula.
The simulation was ran 100 times and the recorded proportions at each iteration 
is used to populate the violin plots.
Similar to figures \ref{fig:markov_vs_des_waiting_time_comparison_overall} and
\ref{fig:markov_vs_des_blocking_time_comparison}, these plots shows a comparison
between the calculated mean proportion of individuals within time using Markov 
chain, using a truncated simulation and using a simulation with infinite
capacity (without the artificial parameters \(N\) and \(M\)).
The proportions generated by the truncated simulation match the ones generated
by the Markov chains model.
Note that this comparison includes both type 1 and type 2 individuals.
A separate comparison of only type 1 and only type 2 individuals can be found 
in appendix~\ref{sec:appendix_additional_figures}.

>>>>

Figure \ref{fig:markov_vs_des_proportion_comparison_overall} shows a comparison
of the mean proportion of individuals within target when using Markov chains 
and discrete event simulation (appendix~\ref{sec:appendix_des}).
The figure is used to demonstrate the accuracy of the formula for the 
proportion of individuals within time of the constructed queueing model
as well as the effect that truncating the model has on the formula.
The simulation was ran 100 times and the recorded proportions at each iteration 
is used to populate the violin plots.
Similar to figures \ref{fig:markov_vs_des_waiting_time_comparison_overall} and
\ref{fig:markov_vs_des_blocking_time_comparison}, these plots shows a comparison
between the calculated mean proportion of individuals within time using Markov 
chain, using a truncated simulation and using a simulation 
without the artificial parameters \(N\) and \(M\).
The proportions generated by the truncated simulation match the ones generated
by the Markov chains model.
Note that this comparison includes both type 1 and type 2 individuals.
A separate comparison of only type 1 and only type 2 individuals can be found 
in appendix~\ref{sec:appendix_additional_figures}.
